\documentclass{resume} 
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} 
\usepackage{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Philip Lowe} % Your name
\address{\href{https://philowe94.github.io/portfolio/}{Portfolio} | \href{https://www.linkedin.com/in/philip-lowe-274b9a9a/}{LinkedIn} | \href{https://github.com/philowe94}{Github}}
\address{(516) 282-5752 \\ philip.lowe94@gmail.com}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }

\urlstyle{same}
\begin{document}

\begin{rSection}{Technical Strengths}

    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
        Languages \        & JavaScript, Ruby                         \\
        Technologies       & React, Redux, Ruby on Rails, TailwindCSS \\
        Tools              & VSCode                                   \\
        Databases          & postgreSQL, MongoDB, noSQL               \\
        Cloud Technologies & Firebase, Google Cloud                   \\
        Version Control    & Git/Github
    \end{tabular}

\end{rSection}

\begin{rSection}{Education}

    {\bf App Academy | New York, NY} \hfill{\em July 2021}

    {\bf Northeastern University | Boston, MA} \hfill{\em May 2017}

\end{rSection}

\begin{rSection}{Work Experience}
    \begin{rSubsection}{Streamline Media Group}{Dec 2021 - Feb 2023 }{Frontend Developer}{}
        \item Developed an internal project management web application using React, Node, and Firebase.
        \item Contributed to both front-end and back-end development, including writing backend functions.
        \item Implemented an automated ad generation tool connecting Contentful with Facebook's Node Marketing API.
    \end{rSubsection}
    \begin{rSubsection}{Town of North Hempstead}{Feb 2018 - Feb 2021 }{IT Webmaster/Help Desk}{}
        \item Built a new version of the town’s intranet website using Wordpress to update the old ASP site.
        \item Managed content on the official public website, providing constituents with updated information about local government services and programs.
        \item Digitally recreated many internal forms to streamline timekeeping processes.
    \end{rSubsection}

\end{rSection}

\begin{rSection}{Projects}
    \begin{rSubsection}{Levernote}
        {\href{https://levernote.herokuapp.com/}{Live Site} |
            \href{https://github.com/philowe94/levernote}{Github}}
        {React/Redux, Ruby on Rails, postgreSQL, Heroku}{}
        \item Created an API interface using Rails for the back end.
        \item Rails queries the SQL database for authentication, notes, and notebooks.
        \item The React front-end displays the current user’s notes and notebooks based on information in a Redux store, which is populated by making API calls to the Rails back-end.
        \item Built as a graduation project for App Academy.
    \end{rSubsection}


    \begin{rSubsection}{Alien Game}
        {\href{https://philowe94.github.io/alien-game/}{Live Site} |
            \href{https://github.com/philowe94/alien-game}{Github}}
        {HTML5, Canvas API, JavaScript}{}
        \item Leveraged HTML Canvas API used to render the game.
        \item Wrote game logic written in pure JavaScript, using Webpack to organize the code into modules.
        \item Authentic gameplay closely matching the GameBoy version.
    \end{rSubsection}

\end{rSection}

\end{document}
